Lapse & Vision Loss PS Analysis

### 2025-08-06 analysis.Rmd
update for twang

```{r init_ps, echo = FALSE}
matchingFormula <- as.formula("ever_lapse_binary ~ 
  baseline_VA_logMAR +
  gender_cat +
  race_ethnic_cat +
  insurance_cat +
  age_cat +
  CCI +
  DCSI +
  other_inject +
  anti_VEGF +
  focal_laser_flag +
  PRP_flag +
  glaucoma_bef_hitplus_cat +
  otherretina_bef_hitplus_cat +
  catsurg_before_hitplus_cat")

@@

```{r analysis_setup}
analysisFormulaSimple <- formula(
  outcome_va_vi_binary ~
    ever_lapse_binary
)

analysisFormulaMiddle <- formula(
  outcome_va_vi_binary ~
    ever_lapse_binary + 
    gender_cat +
    race_ethnic_cat +
    insurance_cat +
    age_cat
)

analysisFormulaFull <- formula(
  outcome_va_vi_binary ~
    ever_lapse_binary + 
    gender_cat +
    race_ethnic_cat +
    insurance_cat +
    age_cat +
    CCI +
    DCSI +
    other_inject +
    anti_VEGF +
    focal_laser_flag +
    PRP_flag +
    glaucoma_bef_hitplus_cat +
    otherretina_bef_hitplus_cat +
    catsurg_before_hitplus_cat
)

>>>>

```{r init_ps, echo = FALSE}
# Get the matching formula from functions.R
matchingFormula <- get_matching_formula()

@@

```{r analysis_setup}
# Get the analysis formulas from functions.R
analysis_formulas <- get_analysis_formulas()
analysisFormulaSimple <- analysis_formulas$simple
analysisFormulaMiddle <- analysis_formulas$middle
analysisFormulaFull <- analysis_formulas$full
